Leadership across cultures and contexts

### 2019-11-25 leadership_across_cultures_contexts.Rmd
Progress...

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=F)
load("Leader2.Rdata")
library(pander)
```

@@

The geographic distribution of the cultures in our sample is displayed in Figure X, with cultures labeled by mode of subsistence and represented by a symbol proportional to the number of documents that provide ethnographic texts for that culture (for details, see Table S1). The `r nrow(leader_text2)` text records from `r length(unique(leadershipdata::documents$d_ID))` unique documents describing `r length(unique(leader_text2$d_culture))` cultures were generally short, with a median word count of X, a mean of X, and standard deviation of X. The vast majority of text records pertained to male leadership (`r male_leader_pct`%) and very few pertained to female leadership (`r female_leader_pct`%), with some records not sex-specific.

@@

For each of the `r length(quality_vars) + length(function_vars) + length(leader_cost_vars) + length(leader_benefit_vars) + length(follower_benefit_vars) + length(follower_cost_vars)` coded variables (see Table X), we computed the percentage of text records that provided support, estimating standard errors using a binomial generalized linear mixed effects model with a random intercept for author nested within culture. See Figure \@ref(fig:varsupport).

```{r varsupport, fig.width=15, fig.height=8, fig.cap="Support for each coded variable. Blue circles: percent of text records with evidence of support. Red triangles: percent of cultures with evidence of support."}
plot.variable.support
```

@@

```{r varsupportcb, echo=FALSE, warning=FALSE, message=F, fig.width=15, fig.height=11, fig.cap="Support for each coded variable. Blue circles: percent of text records with evidence of support. Red triangles: percent of cultures with evidence of support."}
plot.variable.support_costs_benefits
```

@@

A three-rank logistic PCA on the `r length(quality_vars)` coded leader quality variables with $m$ set at `r logpca_model_qualities$m` via cross-validation explained `r signif(logpca_model_qualities$prop_deviance_expl, 3)*100`% of the deviance and converged following `r logpca_model_qualities$iters` iterations. We draw on the first of the three leader quality components for interpretation and additional analyses and identify this component as a *Prestige vs. Dominance* measure. Low values on Leader qualities PC 1 (Prestige vs. Dominance) are strongly associated with the variables *Experienced/accomplished* and *Knowledgeable/intelligence* and moderately associated with *Oratory skill* and *Innovative*. High values are strongly associated with *Polygnous* and *Coercive authority* and moderately associated with *Many children* and *High quality spouse*. Therefore, the "dominance" side of the *Prestige vs. Dominance* component is also closely liked to reproduction. Measures of physical formidability and aggressiveness are also moderately associated with the "dominance" side of this component. See Figure \@ref(fig:qualitiesPCplot).

```{r qualitiesPCplot, fig.width=9, fig.height=7, fig.cap="Logistic PCA loadings of coded leader qualitiy variables on the first of three components."}
qualities_component1_plot
```

Similarly, a three-rank logistic PCA on the `r length(function_vars)` coded leader function variables with $m$ set at `r logpca_model_functions$m` via cross-validation explained `r signif(logpca_model_functions$prop_deviance_expl, 3)*100`% of the deviance and converged following `r logpca_model_functions$iters` iterations. The first Leader functions component distinguishes between interpersonal mediation functions and group organizational and social functions, we define as a *Mediation vs. Organization* measures. Low values on Leader functions PC 1 (Mediation vs. Organization) are strongly associated with the variables *Resolve conflict* and *Provide counsel/direction* and moderately associated with *Political appointments* and *Punishment*, whereas high values are strongly associated with *Social functions* and *Organize cooperation* and moderately associated with *Ritual functions*. See Figure \@ref(fig:functionsPCplot).

```{r functionsPCplot, fig.width=9, fig.height=7, fig.cap="Logistic PCA loadings of coded leader function variables on the first of three components."}
functions_component1_plot
```

@@

```{r, fig.height=20, fig.width=9}
qc_bayes_model_post_plot
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=F)
source('analyses2.R')
library(pander)
```

@@

The geographic distribution of the cultures in our sample is displayed in Figure \@ref(fig:geographic), with cultures labeled by mode of subsistence and represented by a symbol proportional to the number of documents that provide ethnographic texts for that culture (for details, see Table S1). The `r nrow(leader_text2)` text records from `r length(unique(leadershipdata::documents$d_ID))` unique documents describing `r length(unique(leader_text2$d_culture))` cultures were generally short, with a median word count of X, a mean of X, and standard deviation of X. The vast majority of text records pertained to male leadership (`r male_leader_pct`%) and very few pertained to female leadership (`r female_leader_pct`%), with some records not sex-specific.

```{r geographic, fig.width=15, fig.cap="The geographical distributions of cultures in this analysis. Symbol shapes indicate mode of subsistence and symbol size indicates the number of documents available for that culture."}
library(maps)
world_map <- map_data("world")
p_map <- ggplot(world_map, aes(x = long, y = lat)) +
  geom_polygon(aes(group = group), fill="lightgray", colour = "white") +
  geom_point(
    data = leader_cult, 
    aes(
      c_longitude, 
      c_latitude, 
      colour = subsistence, 
      shape = subsistence, 
      size = documents
    )
  ) +
  coord_fixed() +
  labs(x='', y='', shape = 'Subsistence', colour = 'Subsistence', size = 'Documents') +
  guides(shape = guide_legend(override.aes = list(size = 4))) +
  theme_bw(15)
p_map
# ggsave(filename = 'Figures/map.pdf', p_map)
```

@@

For each of the `r length(c(quality_vars, function_vars, leader_cost_vars, leader_benefit_vars, follower_benefit_vars, follower_cost_vars))` coded variables (see Table X), we computed the percentage of text records that provided support, estimating standard errors using a binomial generalized linear mixed effects model with a random intercept for author nested within culture. See Figure \@ref(fig:varsupport).

```{r varsupport, fig.width=15, fig.height=15, fig.cap="Support for each coded variable of leader functions (top) and qualities (bottom). Blue circles: percent of text records with evidence of support (95% CI computed with a binomial mixed effects models with random intercept for author nested within culture). Red triangles: percent of cultures with evidence of support (95% CI computed with a cluster bootstrap)."}
plot.variable.support
```

@@

```{r varsupportcb, echo=FALSE, warning=FALSE, message=F, fig.width=15, fig.height=11, fig.cap="Support for each coded variable for the costs and benefits of leadership and followership. Blue circles: percent of text records with evidence of support (95% CI computed with a binomial mixed effects models with random intercept for author nested within culture). Red triangles: percent of cultures with evidence of support (95% CI computed with a cluster bootstrap)."}
plot.variable.support_costs_benefits
```

## Cluster analyses

```{r qualcluster, fig.cap="Cluster analysis of leader quality variables. Distances are $1 - cor$. Ward agglomeration method. p-values computed with 10,000 bootstrap samples using the pvclust package [@pvclust2015]."}
plot(m_pvclust_qual)
pvrect(m_pvclust_qual, alpha = 0.9)
```

```{r funcluster, fig.cap="Cluster analysis of leader function variables. Distances are $1 - cor$. Ward agglomeration method. p-values computed with 10,000 bootstrap samples using the pvclust package [@pvclust2015]."}
plot(m_pvclust_fun)
pvrect(m_pvclust_fun, alpha = 0.9)
```

@@

A three-rank logistic PCA on the `r length(quality_vars)` coded leader quality variables with $m$ set at `r logpca_model_qualities$m` via cross-validation explained `r signif(logpca_model_qualities$prop_deviance_expl, 3)*100`% of the deviance. We draw on the first of the three leader quality components for interpretation and additional analyses and identify this component as a *Prestige vs. Dominance* measure. Low values on Leader qualities PC 1 (Prestige vs. Dominance) are strongly associated with the variables *Experienced/accomplished* and *Knowledgeable/intelligence* and moderately associated with *Oratory skill* and *Innovative*. High values are strongly associated with *Polygnous* and *Coercive authority* and moderately associated with *Many children* and *High quality spouse*. Therefore, the "dominance" side of the *Prestige vs. Dominance* component is also closely liked to reproduction. Measures of physical formidability and aggressiveness are also moderately associated with the "dominance" side of this component. See Figure \@ref(fig:qualitiesPCplot).

```{r qualitiesPCplot, fig.width=15, fig.height=10, fig.cap="Logistic PCA loadings of coded leader qualitiy variables on the first two components."}
logisticPCA_loadings_plot(logpca_model_qualities, data = pca_data_qualities2)
```

Similarly, a three-rank logistic PCA on the `r length(function_vars)` coded leader function variables with $m$ set at `r logpca_model_functions$m` via cross-validation explained `r signif(logpca_model_functions$prop_deviance_expl, 3)*100`% of the deviance. The first Leader functions component distinguishes between interpersonal mediation functions and group organizational and social functions, we define as a *Mediation vs. Organization* measures. Low values on Leader functions PC 1 (Mediation vs. Organization) are strongly associated with the variables *Resolve conflict* and *Provide counsel/direction* and moderately associated with *Political appointments* and *Punishment*, whereas high values are strongly associated with *Social functions* and *Organize cooperation* and moderately associated with *Ritual functions*. See Figure \@ref(fig:functionsPCplot).

```{r functionsPCplot, fig.width=15, fig.height=10, fig.cap="Logistic PCA loadings of coded leader function variables on the first two components."}
logisticPCA_loadings_plot(logpca_model_functions, data = pca_data_functions2)
```

@@

```{r, fig.height=20, fig.width=9}
# qc_bayes_model_post_plot
```
